% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Economic Calculation and Bayesian Entrepreneurship},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}


\title{Economic Calculation and Bayesian Entrepreneurship}
\author{Tyler J. Brough \and Marc R. Dotson}
\date{2025-05-30}

\begin{document}
\maketitle


We will now proceed to entangle the entire area!

\newpage

\begin{quote}
\emph{The Austrians have played an important role in keeping a set of
ideas alive in the face of a sometimes hostile mainstream. Any progress
forward, however, need not, indeed should not, be a further continuance
of an isolated ``Austrian'' economics\ldots. In fact, it seems
indisputable that scientific understanding would be much improved if at
some point in the future we could genuinely and intelligently say, along
with Milton Friedman, there is no such thing as Austrian economics, only
good economics and bad economics. But this time we would mean that good
economics was an economics not only of preferences and constraints, but
also an economics of time and ignorance.} -- Vaughn (1994)
\end{quote}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\begin{quote}
\emph{Model development is inherently a task of learning under
conditions of unstructured uncertainty.}
\end{quote}

\begin{quote}
\emph{{[}T{]}he ultimate success of these endeavors depends strongly on
creativity, insight, and skill in the process of model creation. As the
model builder entertains new ideas, casting oﬀ those that are not deemed
promising and developing further those that are, he or she is engaged in
a sophisticated process of learning.} -- Geweke (2010)
\end{quote}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\begin{quote}
\emph{Entrepreneurial talent may not be readily amenable to analysis by
tools of modern decision theory. If this be the case, the direction of
emphasis should be clear. We should drop attempts to apply irrelevant
theory rather than to force incompatible material into a received
analytical orthodoxy. It may or may not be possible to ``model''
entrepreneurial choice in a manner that is aesthetically satisfying to
the formal theorist. But any modelling that leaves no room for the
creative and imaginative elements in such choice lends confusion rather
than enlightment to our understanding of the well-springs of economic
progress.} -- Buchanan and Di Pierro (1980)
\end{quote}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\begin{quote}
\emph{Naturally, then, science, understood as the discoverer of absolute
truths, remains} \textbf{\emph{idle}} \emph{for lack of absolute truths.
But this doesn't lead to the destruction of science; it only leads to a
different conception of science. Nor does it lead to a ``devaluation of
science'': there is no common unit of measurement for such disparate
conceptions. Once the cold marble idol has fallen in pieces, the idol of
perfect, eternal and universal science that we can only keep trying to
know better, we see in its place, beside us, a living creature, the
science which our thought freely creates. A living creature: flesh of
our flesh, fruit of our torment, companion in our struggle and guide to
the conquest.} -- de Finetti (1989)
\end{quote}

\newpage

\section{Introduction}\label{introduction}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Reconstructing Pirrong's rational Bayesian.
\item
  Neo-classical misunderstanding of MGRM
\item
  Economic calculation (Misesian microfoundations)
\item
  De Finetti's operational subjective probability
\item
  Bayesian entrepreneurship with Bayesian workflow.
\item
  MGRM's hedging revisited!
\end{enumerate}

\newpage

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-BuchananDiPierroSEJ1980}
Buchanan, James M., and Alberto Di Pierro. 1980. {``{Cognition, Choice,
and Entrepreneurship}.''} \emph{{Southern Economic Journal}} 46 (3):
693--701.

\bibitem[\citeproctext]{ref-DeFinettiERK1989}
de Finetti, Bruno. 1989. {``{Probabilism}: {A Critical Essay on the
Theory of Probability and on the Value of Science}.''}
\emph{{Erkenntnis}} {31} ({2--3}): 169--223.

\bibitem[\citeproctext]{ref-Geweke2010}
Geweke, John. 2010. \emph{{Complete and Incomplete Econometric Models}}.
{Princeton University Press}.

\bibitem[\citeproctext]{ref-Vaughn1994}
Vaughn, Karen I. 1994. \emph{{Austrian Economics in America}: {The
Migration of a Tradition}}. {Cambridge University Press}.

\end{CSLReferences}




\end{document}
